---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

taucharts is an R htmlwidget interface to the TauCharts javascript library

Take a look at the [TODO list](https://github.com/hrbrmstr/taucharts/issues/1) and chip in!

Right now, you can make & customize (including manual color scales & ordered factors + legends + tooltips + trendlines):

- scatterplots
- scatterplot matrices
- line charts
- bar charts (veritical, horizontal & stacked)

Composite plots are on the road map for support but not in the R package yet.

Have a look [on RPubs](http://rpubs.com/hrbrmstr/taucharts) to see what `taucharts` can do!

The following functions are implemented:

- `tauchart`:	Create a new TauChart
- `tau_line`:	Create a TauCharts line chart
- `tau_point`:	Create a TauCharts scatterplot
- `tau_bar`:	Create a TauCharts bar chart (horizontal or vertical)
- `tau_stacked_bar`: Create a TauCharts stacked bar chart (veritcal only)
- `tau_guide_gridlines`:	Control showing of axis gridlines
- `tau_guide_padding`:	Set overall chart padding
- `tau_guide_x`:	Control x-axis padding, label, scale & tick format
- `tau_guide_y`:	Control y-axis padding, label, scale & tick format
- `tau_legend`:	Add a TauCharts tooltip
- `tau_tooltip`:	Add a TauCharts tooltip
- `tau_trendline`:	Add a TauCharts trendline
- `run_tau_app`:	Run a built-in example Shiny app
- `tau_tasks`:  Add post-render JavaScript tasks to taucharts
- `tau_add_css_rule`: Add a CSS rule to the rendered htmlwidget

with many color palette options:

- `tau_color_manual`:	Specify the colors used in the charts
- `tau_color_brewer`:	Use the ColorBrewer palette in the charts
- `tau_color_economist`:	Use the "Economist" palette used in the charts
- `tau_color_few`:	Use the "Few" palette used in the charts
- `tau_color_highcharts`:	Use the HighchartsJS palette used in the charts
- `tau_color_manual`:	Specify the colors used in the charts
- `tau_color_tableau`:	Use the Tableau palette in the charts
- `tau_color_wsj`:	Use the "Wall Street Journal" palette used in the charts

NOTE that there is an issue with custom color palettes and `tau_legend` that is being addressed.

The following datasets are included:

- `cars_data`:  statistics on cars released from 1997 through 2013 (a data frame with 135 rows and 7 variables)

### News

- Version 0.3.0 released : color palettes galore!
- Version 0.3.0.9000 released : `?tau_add_css_rule` (add CSS rules to a chart)
- Version 0.2.6.9000 released : `?tau_tasks` (add JavaScript to a chart)
- Version 0.2.5.9000 released : list & run example Shiny apps - see `?run_tau_app` for more info
- Version 0.2.5.9000 released : stacked bar charts
- Version 0.1.0 released : trendline, tooltips & dev fork (prod is pretty much stable & functional)
- Version 0.0.1.9003 released : facet-based ordering + legends
- Version 0.0.1.9000 released : auto-detects column classes, can add manual colors & faceted plots are now working (see the Rpub for an example)
- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/taucharts")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(taucharts)

# current verison
packageVersion("taucharts")

```

### Test Results

```{r}
library(taucharts)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
